\section{Visualisation}

The major issue we can notice on figure[~\ref{fig:annex_bipartite_network_focus}] is scalability, i.e that if you were to display a large number of developers and modules, it would rapidly become unusable. This is one of the major aspects we wanted to tackle upon creating our own visualisation.
However, we felt that the \emph{focus} metric was not very intuitive, given the complexity of the formulas required to calculate it. Therefore we decided to calculate workload distribution.

\subsection{Workload Distribution}

Workload distribution is the proportion of contributions each developer has made to each component.
We define a contribution as a commit to the repository, and a component as a directory which contains source code.\\

By mining data from git repositories with the Harmony\cite{Harmony} plugin, we were able to calculate the workload distribution, i.e how much did each developer contribute, and to which components?\\
We ran our analysis on two open-source projects: apache/cordova-plugin-contacts\footnote{\url{}}, and apache/cordova-plugin-file-transfer\footnote{\url}}. These projects were selected because of their equivalent sizes in terms of developers and components.\\

Once we had our data, we set upon creating our visualisation. Using a framework extracted from a website\cite{peoplemov}, we created our own website with an interactive visualisation~[see figure \ref{fig:visualiser_default}] of the data we had extracted.\\[0.3cm]

As with the visualisation from \emph{Dual Ecological Mesures in Software Development}\cite{Posnett} the size of a developer represents his total amount of contributions, and the size of a component represents the total amount of contributions it has received. An edge's size also depends on the amount of contributions it represents.
Given that size is not alway the best quantifier of values, that is to say it is often difficult to estimate a value from the size of an element, we created an information redundancy with colours. Blue colours represent developers and components with few contributions, and the spectrum extends to red as that amount increases.
We chose to keep the size of elements, because it makes it easier for people with vision impairments such as colour-blindness to use our tool.
Colour is not a quantifier for edges, but is rather representative of the edge's source and destination.\\

With this visualisation, we made it possible to view one developer's contributions to each component of the project~[see figure \ref{fig:visualiser_dev}] by simply clicking on the developer's name. We also made it possible to select multiple developers at once in order to simultaneously view all their contributions. This allows us to see which developers have worked on the same components, and to detect possible collaborations.\\
Selecting every developer allows us to see how the workload was truly distributed as a whole. It displays a lot of information at once, making it sometimes difficult to discern some of the finer details, but it also allows us to determine how the team interacts.
For instance, it is possible to see if developers tend to work in small teams, or as one large team, and even if developers tend to work alone (if for instance each component has one developer that contributed the major part of it's code).\\[0.3cm]

On the other hand, it is also possible to select components and get the opposite view, i.e all the contributions it has received from each developer. This gives us an easily discernable view of how the team created that component. This is the exact opposite view from selecting every developer, but the information has been filtered down to a simple component, giving less clutter and making it easier to determine which developers have worked on this component, what proportion of their work it represents, as well as what proportion of the component it represents.\\
Selecting multiple components is also possible, and can be used to view how large a proportion of developer's work/time is devoted to a group of components.\\[0.3cm]

Each element also has a popup display which contains the numerical counterparts of the edges, thus making it easy to discern between two edges with similar sizes.
On the component side, the popup indicates the percentage of contributions the top developers have made towards it, sorted in decreasing order. On the developer side, we have the top components to which he has contributed, represented as a percentage of the total amount of his contributions.
Clicking an entry within these popups will isolate the edge it represents~[see figure \ref{fig:visualiser_single_edge}], and clicking it a second time will scroll the page to the opposite end of that edge.
